Create datasets for supplemental analyses

### 2023-03-23 code/translocation_survival_createdata_supp.Rmd
Move dataset creation code chunks out of maps.qmd

```{r load-packages}
library(RPostgreSQL)
library(dplyr) 
library(readr)
library(tidyr)
library(lubridate)
```

@@

>>>>

```{r load-packages}
library(RPostgreSQL)
library(dplyr) 
library(readr)
library(tibble)
library(tidyr)
library(lubridate)
```

@@

## DATASETS 3: Create datasets for maps

### Dataset for map of sample sites for exome capture analysis

Users without the necessary credentials to access the database can access the final dataset at data/maps/exome_points.csv.

```{r}
exome_sites <- read_csv(here::here("data", "maps", "exome_sample_sites.csv"))
n <- nrow(exome_sites)

source("db_connect.R")
exome_points <- dbReadTable(con, c("site")) %>% 
  as_tibble() %>% 
  rename(site_id = id) %>% 
  select(site_id, utme, utmn) %>% 
  inner_join(exome_sites, by = "site_id") %>% 
  add_column(x = sample(-2000:2000, size = n), # Add x-y random noise to obscure exact site locations
             y = sample(-2000:2000, size = n)) %>% 
  mutate(utme_noise = utme + x,
         utmn_noise = utmn + y) %>% 
  select(-utme, -utmn, -x, -y)
source("db_disconnect.R")

write_csv(exome_points, here::here("data", "maps", "exome_points.csv"))
```

## Dataset for map of Yosemite translocation & donor sites

Users without the necessary credentials to access the database can access the final dataset at data/maps/translocation_points.csv.

### Retrieve data & create points layer

```{r}
donor_sites <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  distinct(donor) %>% 
  mutate(site_id = donor, .before = donor) %>% 
  rename(donor_id = donor) %>% 
  add_column(type = "donor")

translocation_sites <- read_csv(here::here("data", "clean", "frog_translocation_final.csv")) %>% 
  distinct(site_id, donor) %>% 
  rename(donor_id = donor) %>% 
  add_column(type = "translocation") %>% 
  bind_rows(donor_sites)

n <- nrow(translocation_sites)

rm(donor_sites)

source("db_connect.R")
translocation_points <- dbReadTable(con, c("site")) %>% 
  as_tibble() %>% 
  rename(site_id = id) %>% 
  select(site_id, utme, utmn) %>% 
  inner_join(translocation_sites, by = "site_id") %>% 
  add_column(x = sample(-2000:2000, size = n), # Add x-y random noise to obscure exact site locations
             y = sample(-2000:2000, size = n)) %>% 
  mutate(utme_noise = utme + x,
         utmn_noise = utmn + y) %>% 
  select(-utme, -utmn, -x, -y)
source("db_disconnect.R")

write_csv(translocation_points, here::here("data", "maps", "translocation_points.csv"))
```
